---
title: "Access spunk:: analysis"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r}
library(targets)
library(tidyverse)
library(spunk)

```


## Installation

The `spunk::` analysis is available at [GitHub](https://github.com/softloud/spunk) with:


Either download the codebase (green `Code` button) as a .zip file or use GitHub command-line interface (`gh cli`)

``` bash
gh repo clone softloud/spunk
```

The raw data are preloaded in the packaged analysis which can be accessed by installing the `spunk::` package:

``` r
# install.packages("devtools")
devtools::install_github("softloud/spunk")
```

`spunk::` is created using `targets::` so that each step in the analysis can be accessed.

```r
install.packages("targets")
```

`spunk::`'s analysis pipeline can be viewed:

```{r message=FALSE}
tar_glimpse()
```

`spunk::` uses the `renv::` package to snapshot the versions of packages used to ensure reproducibility, run this command to load the required packages after opening the R project.

```r
renv::restore()
```



# Raw data

The raw data was last downloaded: 

```{r}
here::here("data", "count_obs.rda") %>%
  file.info() %>%
  pull(ctime)

```

There are four raw datasets preloaded in `spunk::` package: `count_obs`, `morphology_obs`, `motility_obs`, and `volumne_obs` scraped from the googlesheet. 

```{r}
count_obs
```





