---
title: "Machine-readable data"
description: |
  Using these data in future analyses
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(targets)
```

##  About the dataset

The data are provided as part of the packaged analysis.

```{r}
library(spunk)
head(spunk_dat)
```


```{r eval=FALSE}
# use devtools to install a package from github repository
install.packages("devtools")

# install packaged analysis
devtools::install_github("softloud/spunk")

# load packaged analysis
library(spunk)

# load data
data(spunk_dat)

```

```{r}
# columns in data
names(spunk_dat)

```

```{r eval=FALSE}
# description of each column
?spunk_dat

```

The analyses provided in the associated Cochrane review are summaries and overviews. These data provide a means of doing several different future analyses.  

## More specific analyses

Researchers may be interested in investigating one specific intervention from the various interventions in the dataset. Here we provide two tables with summary information about interventions in the first, and class in the second. 

See Summary tables in Living analyses for detailed information about the interventions and classes included in this analysis. 

## Analyse specific classes and interventions


These data can be readily accessed by filtering by intervention using `tidyverse::`.

```{r}
library(tidyverse)
conflicted::conflict_prefer("filter", "dplyr")

spunk_dat %>% 
  filter(intervention == "folic acid")

```

Filters can be combined. For example, we might only interested in studies that reported morphology comparisons with folic acid and placebo.

```{r}
spunk_dat %>% 
  filter(
    outcome == "morphology",
    intervention == "folic acid",
    str_detect(control, "placebo")
  )

```

Or perhaps researchers are interested in all studies that compared coenzyme-q10 with placebo, but allow for combined interventions. 

```{r}
spunk_dat %>% 
  filter(
    str_detect(intervention, "coenzyme-q10")
    )

```

Class-level analysis data can be extracted in a similar manner.

```{r}
spunk_dat %>% 
  filter(
    class == "coenzymes"
  )
```

# Exporting data

These data are then exportable. For example, if we want to export a dataset to a .csv format so that it can be imported into different software platforms.

```{r eval=FALSE}
# create a dataset object to write
coenzyme_dat <-
  spunk_dat %>%
  filter(class == "coenzymes")

# write data to .csv file
write_csv(coenzyme_dat, "coenzyme_dat.csv")

```




