---
title: "Living analysis"
description: |
  Computationally extending the analysis. 
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    toc: true
    toc_float: true
---

# Code reviewers

Thank you for considering helping out with this project. The most important thing to check is that the code does what the manuscript says it does. 

Checking each target in the [`_targets.R`](https://github.com/softloud/spunk/blob/main/_targets.R) file filters to things expected and so forth. 

In this process, adding comments to the code of what your understanding of what it does is very useful. Adding to the documentation of the functions would also be very helpful. Another thing to consider is renaming the targets so that the pipeline conveys the analysis steps clearer. 

Code reviewers may have ideas about the site structure and documentation, as well. 

Do the visualisations answer the questions they are meant to answer? And, are the other analyses that need to be included?

Finally, don't forget to update the DESCRIPTION file with your ORCID as a contributor. 

# Living data analysis 

Code reviewers and other researchers may also wish to extend, that is, patch the script of this analysis. The rest of this document provides guidance on how to do that. A working version of R, and a willingess to learn a small set of functions, is all one needs to have in order to contribute to this analysis.  

Ideally future studies are appended to the dataset so that it remains an up to date repository of all studies examining interventions for male infertility. A good example of a large-scale living analysis is Cochrane's [COVID-NMA](https://covid-nma.com/), applying evidence synthesis to all COVID research as it comes out.

There may be a particular relevant skillset one has developed that would be a small effort but improve the analysis immensely. 

# GitHub

The [`usethis::pr_`](https://usethis.r-lib.org/articles/pr-functions.html) functions are a blessing for this kind of thing. For getting your computer to talk to git, an invaluable resource (every time; every new computer) is [Happy Git with R](https://happygitwithr.com/resources.html).  Just a few functions to smooth the process of forking and contributing to a package. It does require an investment in reading the documentation for those few functions.

[Issues](https://github.com/softloud/spunk/issues) are a great way of pooling knowledge. One person might have an idea for an extension, and another may know how to implement it quickly. 

# Reproducible environment with `renv::`

A frustration for analysts is often version conflicts between R packages. This analysis uses `renv::` to snapshot the versions used for the code. The following function retrieves the correct versions of the packages.

```{r eval=FALSE}
renv::restore()
```


# `targets::` and `tidyverse::`

This analysis is implemented in [`tidverse::`](https://r4ds.had.co.nz/) script, and the analysis is structured as both a package and as a [make-like pipeline](https://books.ropensci.org/targets). 

```{r}
library(targets) # for pipeline
library(tidyverse) # data science functions

```

Note, in particular, that circles are code blocks, and squares represent loops.

```{r message=FALSE}
tar_visnetwork(targets_only = TRUE)
```

Subsections of the pipeline can be viewed by name or by `tidyverse::` selection tools. For example, the pipeline of head to head comparisons can be viewed thus.

```{r message=FALSE}
tar_visnetwork(allow = starts_with("hth"))
```

# Implementing other models

Here is the pipeline for fitting the network meta-analysis models. Functions are documented using `roxygen::2` and can be searched using R, for example `?smd_calc`.

```{r}
# fit dat and fit arms are the most relevant targets for the model implementation
tar_visnetwork(names = c("fit_dat", "fit_arms"))

```

New targets can be appended to the pipeline that calculate the data to be fitted differently, or add a different model algorithm. These can either replace or add to the existing pipeline.
