---
title: "spunk::"
description: |
  Reproducible living analysis and dataset
site: 
  distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

library(tidyverse)
library(sperm)
library(targets)
library(gt)


```



```{r pkg, message=FALSE}
# packages used in this readme
library(tidyverse)
library(sperm)
library(targets)
library(gt)

```

This is the [reproducible packaged living analysis](https://github.com/softloud/spunk) accompanying the Cochrane review:

> Nutritional interventions for male infertility: a systematic review and meta-analysis

which examines nutritional interventions for [sperm](https://www.urbandictionary.com/define.php?term=spunk) motility, sperm morphology, sperm volume, and sperm count.

References for all resources linked in this analysis are provided in a [zotero collection](https://www.zotero.org/groups/4437063/diet_and_infertility_citations). 

## Lead contributors

- Analysis implementation: Charles T. Gray
- Project lead and data extraction: Mohammed Zafar
- Principal investigator: Kerry Mills

```{r echo=TRUE}

citation("spunk")
```
<aside>
Don't know why (NA) is appended to list of authors:
See this [issue](https://github.com/softloud/spunk/issues/7) to help out.
</aside>
